---
title: "大數據分析方法"
author: "曾意儒 Yi-Ju Tseng, 長庚大學資管系"
date: "April 25, 2016"
output: ioslides_presentation
subtitle: "探索性分析 Exploratory Analysis: 圖形分析 - 2"
highlighter: highlight.js
---

## Homework 5
- 分組名單
- 期末報告題目
- 預計分析資料
    - 資料來源
    - 資料格式
- 預計分析議題
    - 假設
    - 預計得到的結果
    - 分析結果可以解決什麼問題
- 5/2 (一) 11:59pm
- http://goo.gl/forms/8UgvNQlHVp

## 靈感！？
- [R Blogger](http://www.r-bloggers.com/)
- [Data Man的資料視覺化筆記](https://www.facebook.com/imDataMan/)
- [Data USA](http://datausa.io/)
- [Randy Olson Twitter](https://twitter.com/randal_olson)
- [Washington Post Information Graphics](http://postgraphics.tumblr.com/)
- [Washington Post | FlowingData](https://flowingdata.com/tag/washington-post/)
- [New York Times | FlowingData](https://flowingdata.com/tag/new-york-times/)
    
## 期中考
- 考卷
- 答案

## 演講
- 大數據在台灣金融行業的應用分享
- 講師：王葆華
- 台灣雲端行動科技公司 與 寶科資訊 負責人

## 上課用程式碼
[Rmd下載](https://github.com/yijutseng/BigDataCGUIM/blob/master/BigData20160425.Rmd)

按Raw，右鍵另存新檔

投影片下載：

[Html下載](https://raw.githubusercontent.com/yijutseng/BigDataCGUIM/master/BigData20160425.html)

按右鍵，另存新檔

# Plotting System--Base

## 探索圖範例：又是大家熟悉的NBA...

```{r message=FALSE,warning=FALSE}
#讀入SportsAnalytics package
if (!require('SportsAnalytics')){
    install.packages("SportsAnalytics")
    library(SportsAnalytics)
}
#擷取2014-2015年球季球員資料
NBA1415<-fetch_NBAPlayerStatistics("14-15")
```


## Simple Summaries of Data - 1

One dimension

* Five-number summary
* Boxplots 箱型圖
* Histograms 直方圖
* Density plot 密度圖
* Barplot 條狀圖


## Five Number Summary

```{r}
#總得分數
summary(NBA1415$TotalPoints)
```



## Boxplot 箱型圖

```{r}
#用總得分數畫箱形圖， col = "blue" 顏色藍色
boxplot(NBA1415$TotalPoints, col = "blue")
```



## Histogram 直方圖

```{r,fig.height=3.5}
#用總得分數畫直方圖， col = "green" 顏色綠色
hist(NBA1415$TotalPoints, col = "green")
```



## Histogram 直方圖

```{r,fig.height=3.5}
hist(NBA1415$TotalPoints, col = "green")
#將總得分數實際的"值"標在直方圖下
rug(NBA1415$TotalPoints)
```



## Histogram 直方圖

```{r,fig.height=3.5}
#breaks = 100 表示將總得分數分為100組
hist(NBA1415$TotalPoints, col = "green", breaks = 100)
rug(NBA1415$TotalPoints)
```



## 層層疊 -1

```{r}
boxplot(NBA1415$TotalPoints, col = "blue")
#在值等於500的地方畫一條橫線
abline(h = 500)
```




## 層層疊 -1

```{r,fig.height=3.5}
hist(NBA1415$TotalPoints, col = "green")
#在值等於500的地方畫一條直線， lwd = 2: 寬度為2
abline(v = 500, lwd = 2)
#在中位數的地方畫一條直線， lwd = :4 寬度為4，顏色為magenta
abline(v = median(NBA1415$TotalPoints), col = "magenta", lwd = 4)
```



## Barplot 條狀圖

```{r}
#col = "wheat"小麥色，標題：main = "Number of Palyers in Each Team"
barplot(table(NBA1415$Team), 
        col = "wheat", main = "Number of Palyers in Each Team")
```



## Simple Summaries of Data - 2

Two dimensions

* Multiple/overlayed 1-D plots (Lattice/ggplot2)
* Scatterplots
* Smooth scatterplots

$> 2$ dimensions

* Overlayed/multiple 2-D plots; coplots
* Use color, size, shape to add dimensions
* Spinning plots
* Actual 3-D plots (not that useful)




## Multiple Boxplots

```{r,fig.width=8,fig.height=3.5}
#預計要做圖的'值'（TotalPoints） ~ 分組依據（Team）
boxplot(TotalPoints ~ Team, data = NBA1415, col = "red")
```



## Multiple Histograms

```{r,fig.width=8,fig.height=3.5}
par(mfrow = c(2, 1), mar = c(4, 4, 2, 1)) #一張圖裡面有2x1個子圖
hist(subset(NBA1415, Team == "SAN")$TotalPoints, col = "green")
hist(subset(NBA1415, Team == "GSW")$TotalPoints, col = "green")
```



## Scatterplot

```{r,fig.height=3}
par(mfrow = c(1, 1)) #一張圖裡面只有一個子圖
#畫x為TotalMinutesPlayed, y為TotalPoints的散佈圖
plot(NBA1415$TotalMinutesPlayed, NBA1415$TotalPoints)
#畫一條橫線h = 500，寬度lwd = 2，樣式lty = 2（虛線）
abline(h = 500, lwd = 2, lty = 2)
```



## Scatterplot - Using Color

```{r,fig.height=3}
#col=NBA1415$Team 用隊伍名稱著色，意指不同隊伍的球員不同色
plot(NBA1415$TotalMinutesPlayed, NBA1415$TotalPoints,col=NBA1415$Team)
abline(h = 500, lwd = 2, lty = 2)
```



## Multiple Scatterplots

```{r,fig.height=3.5,fig.width=8}
par(mfrow = c(1, 2), mar = c(5, 4, 2, 1)) #一張圖裡面有1x2個子圖
with(subset(NBA1415, Team == "SAN"), 
     plot(TotalMinutesPlayed, TotalPoints, main = "SAN"))
with(subset(NBA1415, Team == "GSW"), 
     plot(TotalMinutesPlayed, TotalPoints, main = "GSW"))
```



## Summary

* Exploratory plots are "quick and dirty"

* Let you summarize the data (usually graphically) and highlight any broad features

* Explore basic questions and hypotheses (and perhaps rule them out)

* Suggest modeling strategies for the "next step"


## Further resources

* [R Graph Gallery](http://gallery.r-enthusiasts.com/)
* [R Graph Gallery](http://www.r-graph-gallery.com/all-graphs/)
* [R Bloggers](http://www.r-bloggers.com/)
* [Interactive visualizations with R](http://ouzor.github.io/blog/2014/11/21/interactive-visualizations.html)


# Plotting System -Lattice

## The Lattice Plotting System
包括以下Packaes:

- *lattice*: 包括畫圖相關的函數functions: `xyplot`, `bwplot`, `levelplot`

- *grid*: *lattice* package 的基礎

- 一個函數畫完圖，不能再加標記和文字等



## Lattice Functions

- `xyplot`: 畫散佈圖 scatterplots 
- `bwplot`: 畫盒鬚圖box-and-whiskers plots (“boxplots”)
- `histogram`: 直方圖 histograms
- `stripplot`: 盒鬚圖＋點
- `dotplot`:  dots on "violin strings"
- `splom`: 散佈圖的矩陣
- `levelplot`, `contourplot`: for plotting "image" data



## Lattice Functions

Lattice functions 通常第一個參數是 formula 
```r
xyplot(y ~ x | f * g, data)
```
- We use the *formula notation* here, hence the `~`.

- `y~x`: y-axis~x-axis

- f,g are _conditioning variables_ 
    — optional
    - `*`:  an interaction between two variables

- 第二個參數是資料`data`

- If no other arguments are passed, there are defaults that can be used.


## Simple Lattice Plot

```{r,fig.height=3.5}
library(lattice)
library(datasets)
## Simple scatterplot
xyplot(Ozone ~ Wind, data = airquality) # y~x
```



## Simple Lattice Plot

```{r,fig.width=8,fig.height=3.5}
library(datasets)
library(lattice)
## Convert 'Month' to a factor variable
airquality <- transform(airquality, Month = factor(Month)) 
xyplot(Ozone ~ Wind | Month, #y~x | 分組依據
       data = airquality, layout = c(5, 1)) # 5 rows, 1 column
```

## Lattice Behavior

```{r,fig.height=3.5,fig.width=5}
p <- xyplot(Ozone ~ Wind, data = airquality)  ## Nothing happens!
print(p)  ## Plot appears
```
```{r,eval=FALSE}
xyplot(Ozone ~ Wind, data = airquality)  ## Auto-printing
```


## Lattice Panel Functions

- Lattice functions have a **panel function** which controls what
  happens inside each panel of the plot.

- The *lattice* package comes with default panel functions, but you
  can supply your own if you want to customize what happens in each
  panel

- Panel functions receive the x/y coordinates of the data points
  in their panel (along with any optional arguments) `optional`



## Summary

* Lattice plots 用一個單一函數畫圖 (e.g. `xyplot`)

* 空白和邊緣都有預設值

* 想看一種圖在不同情況下的差異的時候，很適合



